---
title       : Developing Data Products Course Project
subtitle    : Random Distributions
author      : jplcva
job         : Data Science Specialization
logo        : jplcva.png
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, quiz, shiny, interactive]
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Concept

1. Develop a Shiny application hosted on [ShinyApps.io](https://www.shinyapps.io/) from RStudio
2. Publish the Shiny application on [ShinyApps.io Account](https://jplcva.shinyapps.io/Developing-Data-Products-Course-Project/)
3. Illustrate random distributions using a subset of R random generating numbers functions
4. Allow data entry of parameters from the user interface to select the distribution
5. Retrieve generated plots and summaries from the server

--- .class #id 


## User Interface

The user interface where data input is required, is composed of 5 widgets:

* **Choose distribution**: 12 different R random generating numbers distribution functions.
* **Number of observations**: the number of numbers to sample.
* **Set seed**: specify whether a seed value to be entered in the next field.
* `<seed value>`: the seed value.
* **Apply**: enter the required values, before hitting `Apply` to get the results.

```{r opts.label='shiny'}
slidifyUI(
        sidebarPanel(
                selectInput(inputId = "rDist", label = "Choose distribution",
                            choices = c("Bernouilli",
                                        "Binomial",
                                        "Chi-Squared",
                                        "Exponential",
                                        "Geometric",
                                        "Logistic",
                                        "Log Normal",
                                        "Negative Binomial",
                                        "Normal",
                                        "Poisson",
                                        "Student t",
                                        "Uniform")),
                numericInput(inputId = "nObs", label = "Number of observations:",
                             value = 1000, min = 1, max = 100000, step = 1),
                checkboxInput(inputId = "setSeed", label = "Set seed", value = FALSE),
                numericInput(inputId = "seed", label = "", value = 0),
                actionButton(inputId = "applyButton", label = "Apply")
        ),
        mainPanel(
                tabsetPanel(id = "tabset", type = "tabs", selected = NULL,
                            tabPanel("Plot"),
                            tabPanel("Summary"),
                            tabPanel("Model"),
                            tabPanel("About")
                )
        )
)
```

--- .class #id


## Server

```{r, echo=FALSE, results='asis'}
rDist <- c("Bernouilli",
           "Binomial",
           "Chi-Squared",
           "Exponential",
           "Geometric",
           "Logistic",
           "Log Normal",
           "Negative Binomial",
           "Normal",
           "Poisson",
           "Student t",
           "Uniform")
calls <- c("rbinom(n = nObs, size = 1, prob = prob)",
           "rbinom(n = nObs, size = size, prob = prob)",
           "rchisq(n = nObs, df = df)",
           "rexp(n = nObs)",
           "rgeom(n = nObs, prob = prob)",
           "rlogis(n = nObs)",
           "rlnorm(n = nObs)",
           "rnbinom(n = nObs, size = size, prob = prob)",
           "rnorm(n = nObs, mean = mean, sd = sd)",
           "rpois(n = nObs, lambda = lambda)",
           "rt(n = nObs, df = df)",
           "runif(n = nObs)")
df <- as.data.frame(rDist)
df <- cbind(df, calls)
colnames(df) <- c("Distribution", "R Call")
kable(df, format = "html")
```

--- .class #id


## Example

```{r echo=FALSE, results='asis', fig.align='center', fig.height=7, fig.width=10}
require(ggplot2)
nObs <- 1000
mean <- round(runif(1, min = -1 * nObs, max = nObs), 2)
sd <- round(runif(1, min = 1, max = 10), 2)
x <- rnorm(n = nObs, mean = mean, sd = sd)
data <- as.data.frame(x)
g <- ggplot(data, aes(x = x)) +
        geom_histogram(aes(y = ..density.., fill = ..density..), binwidth = 0.1) +
        geom_density(colour = "orangered") +
        geom_vline(xintercept = mean(data$x), colour = "orangered", linetype = "solid") +
        ggtitle(paste(rDist[9], "distribution with", nObs, "observations, mean", mean, "and sd", sd)) +
        theme_bw()
print(g)
```
